\section{Conclusions}
The expiremental set-up made the pixel calibration trivial, the NI Vision software greatly increased the productivity of the workflow. Pictures of the microscopic ruler were easily translated to magnification measurment by the use of edge detection and automatic pixel counting software.\\
NI Vision also proved to be helpfull with determening the resolving power of the multplie magnification objects by being able to export a linetrace of the pixel intensity, this linetrace was easily readable and could thus be plotted in a graph to find the highest and lowest intensity pixel value for each given bar structure from the USAF target. These high and low values allowed for the calculation of our Visibility. The results were as expected apart from the fact that the highest magnification objective had a lower visibility starting point, this however was explaiend by the fact that this object had an overall lower intensity image because its low numerical aperature meant it cought less light.\\
The images of the human hair and optical fiber were made by focussing them with the smallest magnification first and then, when they were in frame and sharp, switching to a higher magnification setup. For the starch particles the same method was used. Both yielded results that matched current literature.\\
Determining the birefringence of the crystal proved quite a bit more difficult than the previous tasks. We found that the knob to adjust the height of the sample had a bit of play, meaning that sizing the layers was hard and thus our results for the layer thicknesses were unreliable at best. This means that our birefringence value has quite a lot of error.\\
\\
Waardes er nog in, resultaten python moeten er nog in.\\
\\








In theConclusies (Conclusions) chapter\\-You give a clear and concise answer to the research question that was formulated in the Intrduction\\-You discuss  to  what  extent,  and  why,  your  findings  do  (not)  agree  with  theory/expectations/earlier  work,   you   discuss   more   speculative   conclusions,   ad   you   may   do   suggestions   for   further   (improved/extended) research.The  Conclusions  should  be  self-contained  and  understandable  for  readers  that  have  only  read  the  introduction  (and  have  not  read the  rest  of  your    report,  do  not  know  the  literature,  do  not  know  the  experimental  setup  and  have  not  read  the  RP  manual).   In  the  Conclusions  chapter,  you  may  not  make  references to graps, tables, equations etc. in the remainder of the report.